Reasoning About a Machine with Local Capabilities

### 2018-05-14 toplas/paper.tex
Add a note to the awkward example proof sketch to point out where the  requirement for memory clearing turns up.

  The next part in the execution is an \texttt{scall}, so according to \sectionname~\ref{sec:reasoning}, we should apply the \texttt{scall} lemma (Lemma~\ref{lem:scall-works}).
  For the sake of presentation, we here sketch some of the things the \texttt{scall} lemma actually takes care of.
  Based on the stack pointer's permission, we know by Lemma~\ref{lem:wl-local} that the capability is local (because it is a system wide assumption that there are no global read/write-local/execute capabilities \textit{c.f.}\ \sectionname~\ref{sec:stack-and-return-pointer}) which means that the region that governs it must be temporary.
  This allows us to construct a world $W_2 \futurestr W_1$ where the stack region of $W_1$ has been revoked\footnote{As a side note, it is also important for the reasoning about $x$ that this is a private future world.}.
  In $W_2$, we replace the stack region of $W_1$ with a temporary static region that governs our stack frame, that is the private registers we push to the stack and the stack recovery code, as well as a standard region $\iota^{pwl}$-region for the part of the stack, we will provide to the callback.
  The static region ensures that our local stack frame remains unchanged during the execution of the callback, and the standard region makes sure that the callback only puts safe values on the stack.
  The callback is global, so it is safe to invoke it in a private future world of $W_1$ (even though the code is unknown, we do not need to use the FTLR because we may assume that the arguments for the invocation of $c_{f4}$ are safe).
  Notice that had the callback been local, this would not be the case, but it would also not be safe to invoke as it might be a stack pointer as discussed in \sectionname~\ref{sec:stack-and-return-pointer}.
  This part corresponds to arguing about Hyp-Callee in the \texttt{scall} lemma.

>>>>

  The next part in the execution is an \texttt{scall}, so according to \sectionname~\ref{sec:reasoning}, we should apply the \texttt{scall} lemma (Lemma~\ref{lem:scall-works}).
  For the sake of presentation, we here sketch some of the things the \texttt{scall} lemma actually takes care of.
  Based on the stack pointer's permission, we know by Lemma~\ref{lem:wl-local} that the capability is local (because it is a system wide assumption that there are no global read/write-local/execute capabilities \textit{c.f.}\ \sectionname~\ref{sec:stack-and-return-pointer}) which means that the region that governs it must be temporary.
  This allows us to construct a world $W_2 \futurestr W_1$ where the stack region of $W_1$ has been revoked\footnote{As a side note, it is also important for the reasoning about $x$ that this is a private future world.}.
  In $W_2$, we replace the stack region of $W_1$ with a temporary static region that governs our stack frame, that is the private registers we push to the stack and the stack recovery code, as well as a standard region $\iota^{pwl}$-region for the part of the stack, we will provide to the callback.
  The static region ensures that our local stack frame remains unchanged during the execution of the callback, and the standard region makes sure that the callback only puts safe values on the stack.
  The callback is global, so it is safe to invoke it in a private future world of $W_1$ (even though the code is unknown, we do not need to use the FTLR because we may assume that the arguments for the invocation of $c_{f4}$ are safe).
  Notice that had the callback been local, this would not be the case, but it would also not be safe to invoke as it might be a stack pointer as discussed in \sectionname~\ref{sec:stack-and-return-pointer}.
  Note also that arguing that the memory satisfies $W_2$ when we invoke the callback only works because we cleared the stack entirely (including the unused part) before the invocation.
  Otherwise, it might contain local values that are only known to be safe in $W_1$, but for which we do not know that they will remain safe in the private future world $W_2$.
  This part corresponds to arguing about Hyp-Callee in the \texttt{scall} lemma.
